---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(readr)
library(ggplot2)
library(gridExtra)
library(xts)
library(dtw)
library(TSclust)
library(dtwclust)
library(TSdist)
```

```{r}
data <- read.csv(file="/Users/123456/Documents/time series/stock-time-series-20050101-to-20171231/all_stocks_2017-01-01_to_2018-01-01.csv", header=TRUE, sep=",")

```


## We create a new datase that only includes difference of open-close price, difference of high-low price and stock volume of each company.
```{r}
data$diff_OC<-data$Open-data$Close
data$diff_HL<-data$High-data$Low

data.new<-data[,c(1,7,6,8,9)]
```

## Data cleaning and normalized, in this part we set all missing data equal to 0.
```{r}
data.new[is.na(data.new)]<-0
data.new$Date <- as.Date(data.new$Date, format = "%Y-%m-%d")

data.new[,c(3,4,5)]<- scale(data.new[,c(3,4,5)])
```

```{r}
# table<-NULL
# for (i in unique(data$Name)){
#     table=rbind(table,data.new[data.new$Name==i,])
# }
```

## In this part, we seperate 31 companies into a stock_list.
```{r}
stock_list <- vector(mode="list", length=length(unique(data.new$Name)))
i = 1
for (c in unique(data.new$Name)){
    stock_list[[i]] <- filter(data.new, Name == c)

    i <- i+1
}
```

## Time Series Plot for Google
```{r}
par(mfrow=c(2,1))
a=stock_list[[29]]
xts1<-xts(a$diff_OC,order.by=a$Date)
xts2<-xts(a$Volume,order.by=a$Date)
ts.plot(xts1,col="red",ylim=c(-10,15),ylab="Dollors")
lines(a$diff_HL,col="blue",ylab="Dollors")
ts.plot(xts2,col="orange",ylab="Quantities")
```

## Time Series Plot for APPLE
```{r}
par(mfrow=c(2,1))
a=stock_list[[3]]
xts1<-xts(a$diff_OC,order.by=a$Date)
xts2<-xts(a$Volume,order.by=a$Date)
ts.plot(xts1,col="red",ylim=c(-2,3),ylab="Dollors")
lines(a$diff_HL,col="blue",ylab="Dollors")
ts.plot(xts2,col="orange",ylab="Quantities")
```

## Time Series Plot for AMAZON
```{r}
par(mfrow=c(2,1))
a=stock_list[[30]]
xts1<-xts(a$diff_OC,order.by=a$Date)
xts2<-xts(a$Volume,order.by=a$Date)
ts.plot(xts1,col="red",ylim=c(-20,20),ylab="Dollors")
lines(a$diff_HL,col="blue",ylab="Dollors")
ts.plot(xts2,col="orange",ylab="Quantities")
```

## For univariate distance measures, we first apply the DTW methods to calculate the distance of open-close price difference.
```{r}
stock_list2 <- vector(mode="list", length=length(unique(data.new$Name)))
i=1
for (c in unique(data.new$Name)){
    stock_list2[[i]] <- stock_list[[i]][,4]
    i=i+1
}

#l=matrix(data=stock_list2,nrow=31,ncol=251)
#names(l)<-c('MMM', 'AXP', 'AAPL', 'BA', 'CAT', 'CVX', 'CSCO', 'KO', 'DIS', 'XOM', 'GE','GS', 'HD', 'IBM', 'INTC', 'JNJ', 'JPM', 'MCD', 'MRK', 'MSFT', 'NKE', 'PFE','PG', 'TRV', 'UTX', 'UNH', 'VZ', 'WMT', 'GOOGL', 'AMZN', 'AABA')
```


```{r}
DM_DTW<-TSDatabaseDistances(stock_list2,distance="dtw")
dist_DTW <- dist(stock_list2, stock_list2, method = "dtw_basic")
DM_EUC<-TSDatabaseDistances(stock_list2,distance="euclidean")
```

```{r}
#DM_DTW
diag(dist_DTW) <- NA
```

```{r}
NN_DTW <- apply(dist_DTW, 1, which.min)
NN_DTW
```

As we can see the 8,22

```{r}
c1=as.ts(stock_list2[[8]])
c2=as.ts(stock_list2[[22]])
c3=as.ts(stock_list2[[7]])
#c4=as.ts(stock_list2[[31]])

par(mfrow=c(3,1))
ts.plot(c1,col="red",ylim=c(-.6,.6),ylab="Dollors",xlab="NKE")
ts.plot(c2,col="red",ylim=c(-.6,.6),ylab="Dollors",xlab="KO")
ts.plot(c3,col="red",ylim=c(-.6,.6),ylab="Dollors",xlab="CSCO")
#ts.plot(c4,col="red",ylim=c(-1,1),ylab="Dollors")
```


## For multivariate distance measures, 
```{r}
N=length(unique(data.new$Name))
T=251

data.multi<-NULL
for (i in 1:N){
    X=t(as.matrix(stock_list[[i]][,c(3,4,5)]))
    data.multi<-rbind(data.multi,X)
}

data.multi2<-t(data.multi)
data.multi2 = (data.multi2 - matrix(rep(1,T),ncol=1)%*%apply(data.multi2,2,mean)) / (matrix(rep(1,T),ncol=1)%*%apply(data.multi2,2,sd))
```

```{r}
data_fft = mvfft(data.multi2)
data_fft = data_fft[c(1:ceiling(251/2)),]

data_per = (1/2/pi/T)*data_fft*Conj(data_fft)
data_per = abs(data_per)

data_cper = NULL
for (p in 1:N) {
  cper_new = (1/2/pi/T)*data_fft[,2*p-1]*Conj(data_fft[,2*p])
  data_cper = cbind(data_cper, cper_new)
}

T2 = dim(data_per)[1]
P2 = dim(data_per)[2]

T3 = dim(data_cper)[1]
P3 = dim(data_cper)[2]

# smoothing periodograms and crossperiodograms
m = 10 ;

data_per_ud = apply(data_per,2,rev) ;
data_per_2 = rbind( rep(0,P2), data_per_ud[(T2-m):(T2-1),], data_per, data_per_ud[2:(m+1),] ) 

data_per_sm = apply(data_per_2,2,cumsum) 
data_per_sm = data_per_sm[(2*m+2):dim(data_per_sm)[1],] - data_per_sm[1:(dim(data_per_sm)[1]-2*m-1),] 
data_per_sm = data_per_sm/(2*m+1) 

data_cper_ud = apply(data_cper,2,rev) 
data_cper_2 = rbind( rep(0,P3), data_cper_ud[(T3-m):(T3-1),], data_cper, data_cper_ud[2:(m+1),] ) 

data_cper_sm = apply(data_cper_2,2,cumsum) 
data_cper_sm = data_cper_sm[(2*m+2):dim(data_cper_sm)[1],] - data_cper_sm[1:(dim(data_cper_sm)[1]-2*m-1),] 
data_cper_sm = data_cper_sm/(2*m+1) 

Q = NULL ;
for (q in 1:(N-1)) {
  for (p in (q+1):N) {
    Q_new1 = abs(data_per_sm[,2*p-1] * data_per_sm[,2*p] - abs(data_cper_sm[,p])^2) 
    Q_new2 = abs(data_per_sm[,2*q-1] * data_per_sm[,2*q] - abs(data_cper_sm[,q])^2) 
    Q_new12 = abs( (data_per_sm[,2*p-1] + data_per_sm[,2*q-1]) * 
                     (data_per_sm[,2*p] + data_per_sm[,2*q]) - 
                     abs(data_cper_sm[,p] + data_cper_sm[,q])^2) 
    Q_new = (Q_new1 * Q_new2) / (Q_new12^2)        
    Q_new = 2^(2*2)*Q_new 
    Q = cbind(Q, Q_new) 
  }
}
Q_st = Q ;

M = T/10 ;

par(mfrow=c(2,1))
plot(Q_st[,1],main="Q_XY(omega_l) for company MMM,AXP",ylab="Q_XY(omega)")
lines(Q_st[,1])
smallest1 <- sort(Q_st[,1],index.return=TRUE)$ix[1:M]
points(smallest1,Q_st[smallest1,1],col="orange")

plot(Q_st[,(2*N-2)],main="Q_XY(omega_l) for company AAPL,BA",ylab="Q_XY(omega)")
lines(Q_st[,(2*N-2)])
smallest2 <- sort(Q_st[,(2*N-2)],index.return=TRUE)$ix[1:M]
points(smallest2,Q_st[smallest2,(2*N-2)],col="orange")
```

```{r}
mean(smallest1)
mean(smallest2)
```


```{r CharTraj}
ret = function(i){
  l = subset(data,data$Name==comp[i])
  l=l$Close-l$Open
  l=scale(l)
  l[145] = 0
  l = l[1:251]
}

```

### Including Plots

![Data Table](/Users/123456/Downloads/screenshot (1).png)

We installed the 'dtwclust' library:

```{r warning=FALSE, message=FALSE}
#install.packages('dtwclust')
library('dtwclust')
```
```{r}
comp = levels(data$Name)
```

To be able to use dist function id dtwclust library, we created a list called list as follows:

```{r}
list = list(ret(1),ret(2),ret(3),ret(4),ret(5),ret(6),ret(7),ret(8),ret(9),ret(10),
            ret(11),ret(12),ret(13),ret(14),ret(15),ret(16),ret(17),ret(18),ret(19),ret(20),
            ret(21),ret(22),ret(23),ret(24),ret(25),ret(26),ret(27),ret(28),ret(29),ret(30),ret(31)
            )

```

We created a distance matrix for two different distance measures, Euclidean and dtw. 
```{r echo=TRUE}
dist_DTW <- dist(list, list, method = "dtw_basic")
dist_Euc <- dist(list, list, method = "euclidean")

```

The distance matrix for DTW is 
```{r echo=FALSE}
dist_DTW
```

The distance matrix for Euclidean distance is
```{r}
dist_Euc
```

```{r}
list=setNames(list,comp)
```

To perform a hierarchical clustering, we used tsclust function in dtwclust package. We have done it for two different distance measurement.
```{r echo=TRUE}
hc_DTW = tsclust(list, type="h", k=5, distance= "dtw_basic")
hc_EUC = tsclust(list, type="h", k=5, distance= "euclidean")

```

This is the dendogram for dtw distance 
```{r echo=TRUE}
 plot(hc_DTW)
```


The dendogram for euclidean distance
```{r echo=TRUE}
 plot(hc_EUC)
```

By looking at the dendograms, we decided to use 5 clusters for both distance measures.
Here are the members of each cluster:
```{r echo=TRUE}
  hc_DTW@cluster	

  hc_EUC@cluster

```

The plot of behavior of the members of each clusters for DTW is as follows:

```{r echo=TRUE}
plot(hc_DTW,type="sc")
```

We observed that companies in the same sector are usually in the same cluster and have similar return behavior.
```{r}
plot(ret(3),type='l',col='blue', main='AMZN vs GOOGL')
lines(ret(11),col='red')
plot(ret(3),type='l',col='blue', main='AMZN vs PG')
lines(ret(25),col='red')
```

```{r}
plot(ret(12),type='l',col='blue', main='GS vs JPM')
lines(ret(17),col='red')
plot(ret(12),type='l',col='blue', main='GS vs NKE')
lines(ret(23),col='red')
```
